---
title: "GP3: Product Feed and Retail Media Setup"
author: "Brian V, Ron S, Alexa B, Kevin B, Sandy Qian Zhu"
date: today
format: 
  html: 
    toc: true
    toc-depth: 4
    number-sections: true
    code-link: true
    embed-resources: true
editor: visual
execute: 
  freeze: auto
---

## Key Question

**How can CPP Farm Store prepare its product information for Google Merchant Center, Amazon Ads, or another retail-media channel?**

## Step-by-Step Guidance

### Step 1: Choose a retail-media or product-listing channel

Your group should focus on at least one channel. Recommended options: \* Google Merchant Center \* Google Shopping / Shopping Ads \* Amazon listing logic \* Amazon Ads concept \* Another approved retail-media platform

> **Note:** Google Merchant Center is recommended because it connects clearly to product feeds, product listings, search visibility, and ecommerce traffic.

### Step 2: Select products

Choose a focused set of products from your Shopify mini-store. Suggested number: \* **Minimum:** 5 products \* **Recommended:** 8–12 products

*Choose products that make sense for online discovery or promotion.*

### Step 3: Create product feed fields

Your product feed should include relevant fields such as: \* Product ID \* Product title \* Product description \* Price \* Availability \* Product category \* Product type \* Brand \* Condition \* Image link or image recommendation \* Landing page URL \* Shipping or pickup information \* Promotion message \* Custom label, if useful

```{r}
#| label: product-feed-data
#| message: false
#| warning: false

library(tibble)
library(knitr)

product_feed <- tibble::tribble(
~`Product ID`, ~`Product title`, ~`Product description`, ~Price, ~Availability, ~`Product category`, ~`Product type`, ~Brand, ~Condition, ~`Image link or image recommendation`, ~`Landing page URL`, ~`Shipping or pickup information`, ~`Promotion message`, ~`Custom label, if useful`,

"SKU-001", "CPP Farm Store Local Gift Basket", "A curated gift basket featuring seasonal treats and locally produced farm products.", "$85.00", "In Stock", "Food, Beverages & Tobacco > Food Items > Food Gift Baskets", "Gift Basket", "CPP Farm Store", "New", "TBD", "TBD", "In-store Pickup Available", "Perfect for holidays and graduation gifts", "Gift Item",

"SKU-002", "CPP Campus Apiary Raw Honey (16 oz)", "Pure, raw honey harvested directly from the Cal Poly Pomona campus apiary.", "$16.00", "In Stock", "Food, Beverages & Tobacco > Food Items > Honey", "Raw Honey", "CPP Farm Store", "New", "TBD", "TBD", "Grab-and-Go Pickup", "Locally harvested honey", "Local Favorite",

"SKU-003", "CPP Seasonal Fresh Produce Box", "A weekly assortment of seasonal fruits and vegetables harvested from the CPP Farm.", "$30.00", "Seasonal", "Food, Beverages & Tobacco > Food Items > Fruits & Vegetables", "Produce Box", "CPP Farm Store", "New", "TBD", "TBD", "Scheduled In-store Pickup", "Farm fresh every week", "Seasonal",

"SKU-004", "CPP Strawberry Jam (12 oz)", "Fresh strawberry jam made from locally grown fruit.", "$9.99", "In Stock", "Food, Beverages & Tobacco > Food Items > Jams & Jellies", "Jam", "CPP Farm Store", "New", "TBD", "TBD", "In-store Pickup Available", "Customer Favorite", "Best Seller",

"SKU-005", "CPP Farm Fresh Eggs (Dozen)", "Farm-fresh eggs produced at Cal Poly Pomona.", "$7.99", "In Stock", "Food, Beverages & Tobacco > Food Items > Eggs", "Fresh Eggs", "CPP Farm Store", "New", "TBD", "TBD", "In-store Pickup Available", "Fresh from the Farm", "Farm Fresh"
)

kable(product_feed)


```

### Step 4: Improve product titles The product titles were improved by adding the

Product titles should be clear, searchable, and customer-friendly. We improved each title by adding the CPP Farm Store brand name, key product attributes, and size or quantity where appropriate. These improvements help increase product visibility in Google Merchant Center and make it easier for customers to identify each product.

```{r}
#| label: improved-product-titles
#| echo: false

library(tibble)
library(knitr)

improved_titles <- tribble(
  ~SKU, ~`Original Title`, ~`Improved Title`,
  "SKU-001", "CPP Farm Store Local Gift Basket", "CPP Farm Store Local Gift Basket – Seasonal Farm Products",
  "SKU-002", "CPP Campus Apiary Raw Honey (16 oz)", "CPP Farm Store Raw Honey (16 oz) – CPP Campus Apiary",
  "SKU-003", "CPP Seasonal Fresh Produce Box", "CPP Farm Store Seasonal Fresh Produce Box – Weekly Harvest",
  "SKU-004", "CPP Strawberry Jam (12 oz)", "CPP Farm Store Strawberry Jam (12 oz) – Locally Made",
  "SKU-005", "CPP Farm Fresh Eggs (Dozen)", "CPP Farm Store Farm Fresh Eggs (1 Dozen)"
)

kable(improved_titles)
```

### Step 5: Improve product descriptions (Brian)

Descriptions should help customers understand value. Strong descriptions may include: \* What the product is \* Key benefits or features \* Suggested use \* Local or seasonal relevance \* Pickup or availability note \* Gift or bundle potential

## Product Feed Data

| Product ID | Product title | Product description | Price | Availability | Product category | Product type | Brand | Condition | Image link or image recommendation | Landing page URL | Shipping or pickup information | Promotion message | Custom label, if useful |
|:-----|:-----|:-----|:-----|:-----|:-----|:-----|:-----|:-----|:-----|:-----|:-----|:-----|:-----|
| **SKU-001** | Gourmet Fruit and Preserve Basket | A luxurious collection of hand-picked seasonal orchard fruits paired perfectly with our signature artisan fruit preserves. Ideal for corporate gifting or holiday family gatherings, this curated basket brings the taste of the local harvest straight to your table. Best enjoyed fresh as a centerpiece display. Available for free standard shipping or local orchard pickup. | 85.00 USD | in stock | Food, Beverages & Tobacco \> Food Items \> Food Gift Baskets | Fruit & Preserve Basket | Orchard Heritage | new | Free standard shipping or local pickup | 10% off with code FRESH10 | Best Seller |  |  |
| **SKU-003** | Heritage Apple Basket | A rustic wooden basket brimming with crisp, heirloom apple varieties hand-picked from our historic centennial orchards. Perfect for autumn baking, homemade cider, or pairing with sharp artisan cheeses, this limited seasonal harvest captures the authentic taste of tradition. Available for quick in-store pickup to ensure maximum freshness. | 45.00 USD | in stock | Food, Beverages & Tobacco \> Food Items \> Fresh Fruit | Fresh Fruit Basket | Orchard Heritage | new | In-store pickup available | 10% off with code FRESH10 | Seasonal |  |  |
| **SKU-005** | Farmhouse Preserve Trio | A beautifully boxed bundle of our three most-loved, small-batch traditional farmhouse jams. Hand-crafted using locally sourced, ripe summer fruits, this set serves as an essential pantry upgrade and an effortless housewarming gift. Perfect for elevating your morning sourdough toast, spreading over warm biscuits, or pairing with afternoon tea. | 35.00 USD | in stock | Food, Beverages & Tobacco \> Food Items \> Condiments & Sauces \> Jams & Jellies | Preserve Trio | Orchard Heritage | new | Free standard shipping | 10% off with code FRESH10 | Gift Bundle |  |  |
| **SKU-008** | Berry Patch Sampler | Celebrate the peak of summer with this vibrant collection of our finest berry jams, jellies, and freshly harvested summer berries. A delightful gift for berry lovers, this sampler is perfect for topping buttermilk pancakes, mixing into morning yogurt bowls, or building a weekend brunch board. Reserve online for fresh local orchard pickup. | 55.00 USD | in stock | Food, Beverages & Tobacco \> Food Items \> Food Gift Baskets | Berry Gift Set | Orchard Heritage | new | In-store pickup available | 10% off with code FRESH10 | Summer Special |  |  |
| **SKU-012** | Limited Run Fig Conserve | An exclusive, small-batch gourmet conserve featuring rich, jammy estate-grown figs slow-cooked with crunchy local walnuts and bright citrus zest. This limited-edition reserve instantly elevates any charcuterie board or premium cheese pairing. A sophisticated addition to holiday gift baskets; available only while supplies last this season. | 25.00 USD | limited availability | Food, Beverages & Tobacco \> Food Items \> Condiments & Sauces \> Jams & Jellies | Limited Edition Conserve | Orchard Heritage | new | Free standard shipping | Limit 2 per customer | Limited Edition |  |  |

### Step 6: Check image readiness

Product images matter for ecommerce and retail media. Identify whether each product has: \* Clear image \* Accurate representation \* Good lighting \* Simple background \* Appropriate size or resolution \* No confusing text overlays \* Consistent style across products

*If images are not available, describe what image would be needed.*

## Step 6: Check Image Readiness

This section evaluates the visual assets for the CPP Farm Store to ensure all online product images meet quality, clarity, and accuracy standards.

### Product Evaluations

#### CPP Craft-Brewed Beer (22 oz Bottle)

- [ ] Product image is clear and easy to identify.
- [ ] The bottle and label are fully visible.
- [ ] The image matches the product being sold.

#### Fresh-Ground Peanut Butter

- [ ] The jar and product label are visible.
- [ ] The image clearly shows the product.
- [ ] The image is appropriate for an online product listing.

#### Fresh-Ground Almond Butter

- [ ] The product label is readable.
- [ ] The jar is clearly displayed.
- [ ] The image represents the product accurately.

#### 100% Raw Local Honey

- [ ] The honey jar is clearly shown.
- [ ] The product label is visible.
- [ ] The image accurately represents the item.

#### Fresh Fruit Gift Packs & Custom Baskets

- [ ] The image shows the contents of the gift basket.
- [ ] The products inside the basket are visible.
- [ ] The image helps customers understand what is included.

### Step 7: Identify feed-quality concerns

Before submitting the product feed to Google Merchant Center, the group should review the product information for accuracy, consistency, and completeness. A complete product feed improves product visibility, reduces the likelihood of feed errors, and creates a better shopping experience for customers.

| Feed-Quality Concern | Issue Identified | Recommendation |
|----------------------------|-----------------------|---------------------|
| Product Images | Image links are currently listed as **TBD** and final product images have not been uploaded. | Upload high-quality product images with good lighting, a clean background, and no distracting text overlays. |
| Landing Page URLs | Product landing page URLs are still marked as **TBD**. | Link each product to its corresponding Shopify product page before submitting the feed. |
| Product Availability | Seasonal products, such as the CPP Seasonal Fresh Produce Box, may not always be available. | Regularly update inventory status using standardized values such as "In Stock," "Out of Stock," or "Seasonal." |
| Shipping and Pickup Information | Some products only mention pickup, while others may be eligible for shipping. | Clearly specify whether each product is available for shipping, in-store pickup, or both. |
| Product Pricing | Prices should be reviewed periodically to ensure they remain accurate. | Keep product prices updated to match the Shopify store and prevent customer confusion. |
| Product Categories | Product categories should accurately match Google Merchant Center requirements. | Review and assign the most appropriate Google product category and product type for each item. |
| Product Consistency | All product information should remain consistent across the Shopify store, Google Merchant Center, and promotional materials. | Verify that product titles, descriptions, pricing, and branding match across every platform. |

#### Overall Feed Assessment

The product feed includes the key fields required for Google Merchant Center, including product IDs, titles, descriptions, pricing, availability, categories, branding, and promotional information. However, several fields still require completion before the feed is ready for submission, including product images and landing page URLs.

Once these remaining fields are completed and the product information is reviewed for accuracy, the feed will provide a strong foundation for Google Shopping listings and future retail media campaigns. Maintaining accurate and consistent product data will also improve customer trust and support better online visibility.

### Step 8: Explain retail-media strategy

This product feed supports the campaign plan by giving each product a distinct role rather than promoting all three equally.

The **CPP Campus Apiary Raw Honey** should be promoted first. It's low-cost, grab-and-go, and has the clearest local story of the three — making it the easiest entry point for someone discovering the store through Google Shopping for the first time, and the best product for building initial search relevance before layering in the others.

The **CPP Seasonal Fresh Produce Box** is best suited for seasonal and recurring campaigns, since its entire appeal is built around what's currently in season on campus. This makes it a natural fit for retargeting ads and ongoing email/social content that gives customers a reason to keep coming back week after week, rather than a one-time purchase.

The **CPP Farm Store Local Gift Basket** is the clearest fit for gift buyers, with the highest price point of the three and a pre-curated format that removes decision fatigue. This is the product to prioritize around key gifting windows — finals week, graduation, and holidays — where a pre-order/pickup model helps address the fulfillment friction our group identified earlier.

Together, the three products cover three different campaign goals — acquisition (Honey), retention (Produce Box), and high-value occasions (Gift Basket) — rather than competing for the same customer at the same time.

---
title: "Retail-Media Strategy & Feed Quality Diagnosis"
subtitle: "CPP Farm Store Evaluation"
date: "2026-07-13"
format:
  html:
    toc: true
    toc-depth: 3
    theme: cosmo
---

## Step 8: Retail-Media Strategy

**Platform:** Google Merchant Center

The CPP Farm Store should prioritize products that are unique, locally produced, and have broad customer appeal.

### Promotion Priorities & Audience Segments

#### Promote First

- **Target Products:** 100% Raw Local Honey, Fresh-Ground Peanut Butter, and Fresh Fruit Gift Packs
- **Rationale:** These items are popular, locally sourced, and appeal to a wide audience.

#### Seasonal Campaigns

- **Target Products:** Fresh Fruit Gift Packs, Custom Gift Baskets, citrus fruit, and holiday baskets.
- **Key Windows:** Ideal for holidays, graduation, Mother’s Day, Thanksgiving, and Christmas.

#### Target Audiences

- **Gift Buyers:** Focus on gift baskets, local honey, jams, and specialty food bundles which make excellent gifts.
- **Students:** Focus on fresh-ground peanut butter, almond butter, honey, and seasonal fruit as affordable, healthy options for CPP students.

#### Logistics & Fulfillment Optimization

- **Store Pickup / Local Shopping:** Fresh fruit, nut butters, honey, and gift baskets are best promoted for local pickup because they are fresh products available directly at the CPP Farm Store.

------------------------------------------------------------------------

## Overall Feed Issues

Before launching aggressive campaigns, the following structural feed issues must be resolved: \* Some products have limited descriptions. \* Product images should have consistent backgrounds and sizing. \* Product titles could include brand, size, and important keywords. \* Availability should clearly state “In Stock” or “Seasonal.” \* Some products do not have dedicated landing pages. \* Shipping or pickup information should be clearly stated.

------------------------------------------------------------------------

## Feed Quality Diagnosis by Product

### CPP Craft-Brewed Beer (22 oz Bottle)

- [ ] Missing a detailed product description.
- [ ] Should include age restriction information.
- [ ] Product image could be improved with a consistent background.
- [ ] Availability should be clearly listed.

### Fresh-Ground Peanut Butter

- [ ] Description should include ingredients and freshness.
- [ ] Add serving suggestions and nutritional highlights.
- [ ] Include a high-quality product image.
- [ ] Clearly indicate stock availability.

### Fresh-Ground Almond Butter

- [ ] Add product benefits and ingredient information.
- [ ] Include suggested uses.
- [ ] Improve product image consistency.
- [ ] Add pickup availability.

### 100% Raw Local Wildflower Honey

- [ ] Add information about local sourcing and benefits.
- [ ] Include jar size or weight.
- [ ] Improve product description with keywords.
- [ ] Clearly indicate availability.

### Fresh Fruit Gift Packs & Custom Baskets

- [ ] Needs a dedicated product page.
- [ ] Add pricing information.
- [ ] Specify seasonal availability.
- [ ] Include multiple product images showing basket options.

## Overall Feed Quality Concerns

::: callout-warning
### Critical Optimizations Needed

1.  **Incomplete Descriptions:** Several products lack comprehensive detail.
2.  **Product Titles:** Titles should standardized to include the store name, product type, and size.
3.  **Images:** Images require consistent backgrounds and high-resolution formatting.
4.  **Availability status:** Must explicitly clarify whether products are "In Stock" or "Seasonal."
5.  **Fulfillment:** Shipping and pickup options must be dynamically included for every product.
6.  **Web Infrastructure:** Missing dedicated landing pages for specific promotional assets must be built.
:::

------------------------------------------------------------------------

## Recommendations: Prioritized Product Launch

Based on demand, margins, and operational readiness, products should be prioritized for promotion in the following order:

### 1. 100% Raw Local Honey

- High search demand
- Distinctively local product
- Great gift item
- Long shelf life and easy logistics

### 2. Fresh-Ground Peanut Butter

- High affordability
- Healthy option
- Strong appeal to both students and visiting families

### 3. Fresh Fruit Gift Packs

- High seasonal conversion rate
- Excellent for holidays and special occasions
- Drives higher average order value (AOV)

### 4. Fresh-Ground Almond Butter

- Premium specialty product margin
- Appeals strongly to health-conscious shoppers

### 5. CPP Craft-Brewed Beer

- Highly unique campus identity product
- Strong appeal to alumni and campus visitors *(Promote only where legally permitted by platform policies)*